Refinements for open pNets

### 2021-07-29 2021-Refinement/paper/refinementarticle.tex
relecture hole - = simu

We generalise simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
\begin{definition}[Hole-equal simulation]
Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold: 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
	\mpar{\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}
	\end{array}} \\
	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
\end{multline*}
\end{definition}
Note in this definition, instead of matching an instantiated transition of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$. Note also the second part of the conjunction of condition 2 expresses the deadlock reduction between automata.

Intuitively, this means that for every pair of related
states $(s_1,s_2)$  of the two automata, and for every each transition of the first automaton from $s_1$, there is a matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.

>>>>

We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
\begin{definition}[Hole-equal simulation]
Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold: 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
	\mpar{\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \\[-10pt]
		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}\right)
	\end{array}} \\
	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
\end{multline*}
\end{definition}
Note in this definition, instead of matching an instantiated transition of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$. Note also the second part of the conjunction of condition 2 expresses the deadlock reduction between automata.

Intuitively, this means that for every pair of related
states $(s_1,s_2)$  of the two automata, and for every  transition of the first automaton from $s_1$, there is a set of matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.
